Re-fit

### 2022-08-18 scripts/r/04_refit/refit_jvc.Rmd
edits

#
# JVC refits
#
MSA_gymnothorax_spinulosus_df <- gymnothorax_spinulosus_int %>% 
  mutate(measure_z = (measure - mean(measure)) / sd(measure),
    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean), 
    typ_mean_z = (typ_mean - mean(typ_mean)) / sd(typ_mean)) %>% 
  filter(condition == "AF")

gymnothorax_spinulosus_1_intdiff_con <- brm(
  measure_z ~ effect_con * typ_mean_z + 
    (1|target_colour) + 
    (1|speaker), 
  data = MSA_gymnothorax_spinulosus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  control = list(max_treedepth = 14), 
  file = here("data", "analyses", "models", "gymnothorax_spinulosus_1_intdiff_con")
  )

>>>>

#
# JVC refits
#
MSA_gymnothorax_spinulosus_df <- gymnothorax_spinulosus_int %>% 
  mutate(measure_z = (measure - mean(measure)) / sd(measure),
    effect_con = (typ_mean - mean(typ_mean)) / sd(typ_mean), 
    condition_s = as.factor(condition),
    condition_s = C(condition_s, sum))
#  filter(condition == "AF")

gymnothorax_spinulosus_1_intdiff_con <- brm(
  measure_z ~ effect_con * condition_s + 
    (1|target_colour) + 
    (1|speaker), 
  data = MSA_gymnothorax_spinulosus_df, 
  cores = 4, threads = threading(2, grainsize = 100), 
  backend = "cmdstanr", seed = 06022016, 
  control = list(max_treedepth = 14), 
  file = here("data", "analyses", "models", "gymnothorax_spinulosus_1_intdiff_con")
  )
